Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
lammps charts merge solved

\subsection{Managing remote GPUs with OpenStack}
The main idea is to move from the original Openstack architecture (see Figure~\ref{fig:os-orig}) to a solution where a new shared service takes part into the architecture and is responsible for all related to GPU accelerators (see Figure~\ref{fig:external}).
This new service would bring more flexibility when managing GPUs and new working modes for GPGPU computation in the Cloud.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os-orig.png}
  \caption{Openstack Architecture.}
  \label{fig:os-orig}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os1.jpg}
  \caption{Openstack with our GPGPU Service.}
  \label{fig:external}
\end{figure}

>>>>

\subsection{Managing remote GPUs with OpenStack}
The main idea is to move from the original Openstack architecture (see Subfigure~\ref{subfig:os-orig}) to a solution where a new shared service takes part into the architecture and is responsible for all related to GPU accelerators (see Subfigure~\ref{subfig:os-mod}).
This new service would bring more flexibility when managing GPUs and new working modes for GPGPU computation in the Cloud.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

\begin{figure}[htb]
  \centering
  \subfigure[Original in version XXXXXXXXXXXXXXXXXXXXXX]{
    \includegraphics[width=\linewidth]{images/os-orig.png}
    \label{subfig:os-orig}
   }
   \quad
  \subfigure[With GPGPU developed module]{
    \includegraphics[width=\linewidth]{images/os1.jpg}
    \label{subfig:os-mod}
   }
  \caption{Openstack Architecture}
  \label{fig:os}
\end{figure}
